Analysis and figures

### 2024-09-23 Manuscript.qmd
Converted most of analysis supplement

  A key aim of this review is to explore how users of DOMs have incorporated covariates into their models to describe variation in occupancy through space and time. Broadly speaking, model complexity in DOMs tends to be low, with relatively few covariates considered for inclusion and most relationships represented as simple linear terms. Considerable variation also exists in the procedures used for covariate selection, and limited research has been conducted on how these choices may influence model performance and inference. Furthermore, only a fraction of articles appear to evaluate models (either by goodness-of-fit testing or prediction validation). Likewise, little guidance exists on how to approach this task in DOMs. These uncertainties in the modelling process should be key priorities for future research on DOMs given their increasing use in applied ecological research.

bibliography: references.bib
csl: apa.csl
---

@@

$$
\begin{align*}
z_1 &\sim Bernoulli(\psi_1)\\\\
z_t &\sim Bernoulli(\psi)\\
&\psi = z_{t-1}(1-\epsilon)+(1-z_{t-1})\gamma
\end{align*}
$$ {#eq-occupancy}

@@

While most articles in our sample fit a model to a single species, 41 fit models to multiple species either as independent models or explicitly multi-species implementations. The multi-species models use various extensions of the conventional DOM, including hierarchical models which fit hundreds of species in a single implementation with species-level effects[@dorazio2010; @hendershot2020], as well as explicit interaction models which estimate conditional occupancy, colonisation, extinction, and detection probabilities [@lesmeister2015; @fidino2019]. Rather than using multi-species models, several other authors fit large numbers of independent models to different species [@peach2019; @otto2012]. Working with large numbers of taxa does raise additional challenges, as the level of complexity which can realistically be considered for each individual taxon is likely to be reduced for the sake of practicality.

![A) Study areas: Data for a majority of studies were collected from study locations in the United States. The size of study areas was log-normally distributed, with the median study area falling between 1000 and 10000 square kilometres. B) Study taxa: Most species modelled in our sample were terrestrial vertebrates including birds, mammals, or herptiles. 55 articles fit models to only a single taxa, 30 fit independent models to multiple taxa, and 11 fit multi-species models with explicit interactions between taxa. C) Survey methods: Approaches to data collected were varied and included conventional surveys like point counts and transects as well as more modern methods like camera traps and acoustic monitors. 13 articles incorporated data from citizen science projects. Project scale was also variable, with the median study running for 6 years and covering 101 sites.](Figures/ReviewBox.png){#fig-StudyDetails}

The presence/absence data required for DOMs has come from a breadth of different sources and detection methods. In our sample 79% of articles used human observational data, 9% used live-trapping methods, and 14% used detections from camera traps. Several articles also use citizen-science data to build detection histories, including @zuckerberg2011's model using bird-feeder data and @warrier2020's using citizen reports of tiger signs. Using citizen-science data may require additional consideration of assumptions (particularly false-positives), as discussed in greater detail by @cruickshank2019. Within these broad categories of detection method there is additional diversity, with several studies using unique survey methods determining the presence of a species at a location. For example, in the only application of a DOM for a marine species in our sample, @pendleton2022 uses aerial transects broken up into grid cells to observe whale occupancy; and @marescot2020's fits a unique 'multi-species' model treating poachers and using ranger reports to create detection histories.

Notably, many of these studies use data which were not originally collected in a robust design framework for occupancy modelling. In these articles, authors formatted their data into a hierarchical format post-hoc using a variety of methods. Some defined primary seasons as a discrete time interval, treating all surveys occurring within the season as secondary occasions; others defined sites as larger grid cells, treating any survey falling within the grid as a spatial replicate. These manipulations permit authors to use data which far predate the DOM, with one study using surveys conducted by Joseph Grinnell in 1908 to model century-long changes in occupancy [@riddell2021].

Additionally, not all articles rely on a single source of detection data - some integrate multiple sources of data to maximise sample size, combining data from camera traps, sign surveys, and citizen science reports. These integrated detection method models do require additional care and consideration; users must ensure that different detection methods represent comparable spatial and temporal scales, and that any variation in perceptibility between detection methods is accounted for [@warrier2020; @pitman2017]. A special case exists when different detection methods are used where one has the potential for false positive detections; e.g., where less-certain citizen science detections are combined with certain detections from field surveys. In this context, the certain detections are used to help account for false-positive detection probability, as in @miller2011's study integrating GPS collars and hunter reports to estimate wolf occupancy in Montana.

The flexibility in the data used for DOMs, including the model structure and the scale of observations, is not amenable to a one-size-fits-all definition of occupancy. Users of DOMs must carefully consider precisely what they are modelling and address questions on the scale represented by their model [@chave2013]. Intepretation and drivers of occupancy may differ depending on whether a site is represented by a single point on the landscape or as a grid cell, with the former likely to depend on more local, small scale factors rather than landscape-level trends [@stevens2019]. This is also true for the temporal scale of occupancy: whether a site is occupied within a week or within a year leads to vastly different conceptions of occupancy. This idea is particularly relevant in cases where the selection of season length *is* to some extent arbitrary, as with camera-trap or bioacoustic data where continuous recordings can be broken down into distinct 'seasons' of any length. DOMs are well suited to these data types [@balantic2019], and the proliferation of autonomous survey techniques provides novel opportunities for analysis that is simply not possible with human-collected data. For example, @kleiven2020 and @mölle2022 divide their camera trap records into seasons of just a few days. While this provides interesting insights of occupancy at extremely fine temporal scale, further research may be needed on how to determine appropriate season and survey durations with respect to research questions and the closure assumption.

@@

The largest differences between the frequentist and Bayesian models in our sample lie in their approaches to model selection. Where 94% of frequentist models perform some manner of model selection to determine covariate inclusions for their models, only 36% of Bayesian models do so, with the majority instead fitting a single model defined *a priori*. Methods used for model selection vary considerably both within and between modelling frameworks. For frequentist models, the most popular and conventional approach to model selection as used in 43% of articles involves the creation of a fully pre-defined model set containing some number of hypothesis candidate models, where the best model is selected according to the lowest AIC score. Most frequentist studies which do not follow this protocol instead use procedural model selection methods (39% of articles), where the structure for each model parameter is fit one-by-one. For example, this protocol might first identify the best structure for detection probability before moving on to initial occupancy and so on. A smaller portion of frequentist studies (9%) use more unique approaches, fitting simpler models such as single season occupancy models for candidate covariates to identify the most informative terms to use in a DOM. Across all frequentist implementations, 71% of articles conduct multi-model inference and model-averaging using AIC weights [@burnham2004].

Those Bayesian models which *do* perform model selection tend to take distinctly different approaches, with largely idiosyncratic methods across these studies. While direct comparison of model fit is rare, it is feasible — @urban2023 identifies the best model from a Bayesian candidate set using the predictive performance on both in and out-of-sample validation data. Another approach used by @cook2022 fit a global model including all covariates before removing each covariate where the 95% credible interval of the posterior distribution overlapped zero and refitting the model. @ahumada2013 takes a hybrid approach, in which model selection is conducted by a procedural method in the frequentist framework before refitting the best structure in a Bayesian model.

Limited research has been conducted on advantages of different methods for covariate selection in DOMs, and there is surely no one-size-fit all approach which will be appropriate for all possible use-cases. However, it is important to consider the implications of the different model selection approaches in common usage, and research from the SDM literature highlights how covariate selection can influence our interpretation of model outputs [@brodie2020]. Within the occupancy modelling literature, @stewart2023's article on covariate selection in single-season occupancy model discusses important attributes of the information-criteria approaches widely used in frequentist models in our review, noting that these approaches can lead to inaccurate estimates and influence model inference. @morin2020's work raises different concerns on procedural model selection methods, demonstrating how the fine details of modelling protocols can determine whether the best-fitting possible model is identified and which covariates appear in final models. The literature on performance of Bayesian model selection methods is more sparse, although @hooten2015's guide to Bayesian model selection in ecology is a valuable resource for possible methods of fitting those models.

With few exceptions, most of the model selection methods identified in our review are designed only to identify the best model of those considered, and do not necessarily guarantee that selected models are well-fit to the data. Assessment of the performance of DOMs generally requires additional steps, and the best ways to achieve this are not necessarily clear. There is no broadly-accepted goodness-of-fit test for dynamic occupancy models, although @mackenzie2004 describes an approach for single-season occupancy models using a parametric bootstrap which can been extended to DOMs; this test is implemented in the *AICcModAvg* and *unmarked* R packages. @kéry2021 describe the test and present an alternative based on separately assessing fit to static and dynamic components of the model. In Bayesian implementations, posterior predictive checks offer means to assess model fit [@gelman2014]. @broms2016 discusses possibilities for model evaluation in the Bayesian context focusing on single-season multi-species occupancy models but extensions of their approach may also be applicable to the DOM. As in other hierarchical models, model evaluation for DOMs can in general can be difficult and somewhat uncertain compared to other model types, as the primary response variable of interest (species occupancy) is a latent variable where the true state is generally not known. Predictive performance evaluation is thus typically based on *observed* occupancy data, where a DOM is used to simulate detection histories to be compared with field survey results.

Perhaps as a result of this uncertainty, assessment of model fit and model performance was rare amongst the articles in our sample. Only 19% of studies tested for goodness-of-fit, and just 10% calculated predictive performance. These rates are considerably lower than for models like SDMs; for which @araújo2019's review of applications found closer to 50% articles testing both fit and performance.

@@

Studies in our sample were classified according to their objectives as stated by authors to explore the use-cases which DOMs have been applied for. These objective categories were non-exclusive, and many studies fell into multiple categories; the frequency at which studies pursued each of these objectives is shown in @fig-objectives A. Across our study period DOMs have been frequently employed to observe trends in species occupancy, to explore relationships between environmental factors and occupancy, and, increasingly often, to make predictions of occupancy spatially to unsurveyed locations or temporally to hypothetical future conditions. Within each of these broad categories lies even more variation in objectives, emphasising the DOM's flexibility as a tool for making ecological inference in diverse contexts.

Many articles in our sample used the DOM seeking to monitor trends in occupancy state through time. These studies include @ahumada2013's paper assessing populations trends of 13 forest mammals and @scott2015's assessment of the conservation status of the endangered flattened musk turtle. These studies offer valuable insights on the state of species across landscapes and through time, demonstrating DOMs' suitability for many monitoring oriented projects — including those where many species need to be assessed at once. Other articles were more focused on examining the factors which influence species occupancy, either testing a pre-specified hypothetical relationships or taking a broader tack to identify drivers of occupancy without preconception. The distinction between the two is important, as it guides which covariates may be considered and how model selection may be used to fit models. Many of these studies target core conservation priorities for their focal species, like @olson2005's early DOM assessing the influence of barred owls on threatened spotted owl. Explorations of these pivotal relationships are important for guiding management action, and may also be used to test the effectiveness of these actions as in @miller2023's study on American Kestrel nest boxes. In scenarios where less is known about species habitat preference, DOMs may be used to examine the influence of a wider variety of factors as illustrated in @huber2017's study testing the relative influence of dozens of habitat covariates on Wood warbler occupancy. In recent years, increasing numbers of articles have used to DOM to generate predictions of species occupancy. As examples, @mcgowan2020 provides projections for the threatened Black rail under multiple management scenarios, and @pollentier2021 generates maps of distributions resembling those made with SDMs, outputs which can immediately be used by managers to inform action.

>>>>

  A key aim of this review is to explore how users of DOMs have incorporated covariates into their models to describe variation in occupancy through space and time. Broadly speaking, model complexity in DOMs tends to be low, with relatively few covariates considered for inclusion and most relationships represented as simple linear terms. Considerable variation also exists in the procedures used for covariate selection, and limited research has been conducted on how these choices may influence model performance and inference. Furthermore, only a fraction of articles appear to evaluate models (either by goodness-of-fit testing or prediction validation). Likewise, little guidance exists on how to approach this task in DOMs. These uncertainties in the modelling process should be key priorities for future research on DOMs given their increasing use in applied ecological research.
---

@@

$$
\begin{align*}
z_1 \sim& Bernoulli(\psi_1)\\\\
z_t \sim& Bernoulli(\psi)\\\\
&\psi = z_{t-1}(1-\epsilon)+(1-z_{t-1})\gamma
\end{align*}
$$ {#eq-occupancy}

@@

While most articles in our sample fit a model to a single species, 41 fit models to multiple species either as independent models or explicitly multi-species implementations. The multi-species models use various extensions of the conventional DOM, including hierarchical models which fit hundreds of species in a single implementation with species-level effects[@dorazio2010; @hendershot2020], as well as explicit interaction models which estimate conditional occupancy, colonisation, extinction, and detection probabilities [@lesmeister2015; @fidino2019]. Rather than using multi-species models, several other authors fit large numbers of independent models to different species [@peach2019; @otto2012]. Working with large numbers of taxa does raise additional challenges, as the degree to which models are tailored to the taxa is likely to be limited for the sake of practicality.

![A) Study areas: Data for a majority of studies were collected from study locations in the United States. The size of study areas was log-normally distributed, with the median study area falling between 1000 and 10000 square kilometres. B) Study taxa: Most species modelled in our sample were terrestrial vertebrates including birds, mammals, or herptiles. 55 articles fit models to only a single taxon, 30 fit independent models to multiple taxa, and 11 fit multi-species models with explicit interactions between taxa. C) Survey methods: Approaches to data collected were varied and included conventional surveys like point counts and transects as well as emerging methods like camera traps and acoustic monitors. 13 articles incorporated data from citizen science projects. Project scale was also variable, with the median study running for 6 years and covering 101 sites.](Figures/ReviewBox.png){#fig-StudyDetails}

The presence/absence data required for DOMs has come from a breadth of different sources and detection methods (@fig-StudyDetails, panel C). In our sample 79% of articles used human observational data, 9% used live-trapping methods, and 14% used detections from camera traps. Several articles also use citizen-science data to build detection histories, including @zuckerberg2011's model using bird-feeder data and @warrier2020's using citizen reports of tiger signs. Using citizen-science data may require additional consideration of assumptions (particularly false-positives), as discussed in greater detail by @cruickshank2019. Within these broad categories of detection method there is additional diversity, with several studies using unique survey methods determining the presence of a species at a location. For example, in the only application of a DOM for a marine species in our sample, @pendleton2022 use aerial transects broken up into grid cells to observe whale occupancy; and @marescot2020 fit a unique 'multi-species' model treating poachers as a taxon and using ranger reports to create detection histories.

Notably, many of these studies use data which were not originally collected in a robust design framework for occupancy modelling. In these articles, authors formatted their data into a hierarchical format post-hoc using a variety of methods. Some defined primary seasons as a discrete time interval, treating all surveys occurring within the season as secondary occasions; others defined sites as larger grid cells, treating any survey falling within the grid as a spatial replicate. These manipulations permit authors to use data which predate the DOM, with one study using surveys conducted by Joseph Grinnell in 1908 to model century-long changes in occupancy [@riddell2021].

Additionally, not all articles rely on a single source of detection data - some integrate multiple sources of data to maximise sample size, combining data from camera traps, sign surveys, and citizen science reports. These integrated detection method models do require additional care and consideration; users must ensure that different detection methods represent comparable spatial and temporal scales, and that any variation in perceptibility between detection methods is accounted for [@warrier2020; @pitman2017]. A special case exists when different detection methods are used where one has the potential for false positive detections; e.g., where less-certain citizen science detections are combined with certain detections from field surveys. In this context, the "certain" detections are used to help account for false-positive detection probability, as in @miller2011's study integrating GPS collars and hunter reports to estimate wolf occupancy in Montana.

The flexibility in the data used for DOMs, including the model structure and the scale of observations, is not amenable to a one-size-fits-all definition of occupancy. Users of DOMs must carefully consider precisely what they are modelling and address questions on the scale represented by their model [@chave2013]. The interpretation of what 'occupancy' means and the factors which drive it may differ depending on the scale of what is considered a site, and how that relates to the ecology of a species. This is also true for the temporal scale of occupancy: whether a site is occupied within a week or within a year leads to vastly different conceptions of occupancy. This idea is particularly relevant in cases where the selection of season length *is* to some extent arbitrary, as with camera-trap or bioacoustic data where continuous recordings can be broken down into distinct 'seasons' of any length. The DOM may be readily applied to these data types [@balantic2019], and the proliferation of autonomous survey techniques provides novel opportunities for analysis that is simply not possible with human-collected data. For example, @kleiven2020 and @mölle2022 divide their camera trap records into seasons of just a few days. While this provides interesting insights of occupancy at extremely fine temporal scale, further research could help provide general guidance on determining appropriate season and survey durations with respect to research questions and the closure assumption.

@@

The largest differences between the frequentist and Bayesian models in our sample lie in their approaches to model selection. Where 94% of frequentist models perform some manner of model selection to determine covariate inclusions for their models, only 36% of Bayesian models do so, with the majority instead fitting a single model defined *a priori*. Methods used for model selection vary considerably both within and between the two modelling frameworks (@tbl-modelling). For frequentist models, the most popular and conventional approach to model selection as used in 43% of articles involves the creation of a fully pre-defined model set containing some number of hypothesis candidate models, where the best model is selected according to the lowest AIC score. The next most popular method in frequentist studies is to use procedural model selection methods (39% of articles), where the structure for each model parameter is fit one-by-one. For example, this protocol might first identify the best structure for detection probability before moving on to initial occupancy and so on. The remainder of frequentist studies (9%) use a variety of approaches, such as fitting simpler models like single season occupancy models to identify the most informative terms to use in a DOM. Across all frequentist implementations, 71% of articles summarise a final subset of models using multi-model inference and model-averaging with AIC weights [@burnham2004].

Those Bayesian models which *do* perform model selection tend to take various approaches, with largely idiosyncratic methods across these studies. While direct comparison of model fit is rare in Bayesian methods, it is feasible — @urban2023 identifies the best model from a Bayesian candidate set using the predictive performance on both in and out-of-sample validation data. Another approach used by @cook2022 fit a global model including all covariates before removing each covariate where the 95% credible interval of the posterior distribution overlapped zero and refitting the model. @ahumada2013 takes a hybrid approach, in which model selection is conducted by a procedural method in the frequentist framework before refitting the best structure in a Bayesian model.

Limited research has been conducted on advantages of different methods for covariate selection in DOMs, and there is unlikely to be a one-size-fits-all approach which will be appropriate for all possible use-cases. However, it is important to consider the implications of the different model selection approaches in common usage, and research from the SDM literature highlights how covariate selection can influence our interpretation of model outputs [@brodie2020]. Within the occupancy modelling literature, @stewart2023's article on covariate selection in single-season occupancy models discusses important attributes of the information-criteria approaches widely used in frequentist models in our review, noting that these approaches can lead to inaccurate coefficient estimates that may influence model inference. @morin2020's work raises other concerns on procedural model selection methods, demonstrating how the fine details of modelling protocols can determine whether the best-fitting possible model is identified and which covariates appear in final models. The literature on performance of Bayesian model selection methods is more sparse, although @hooten2015's guide to Bayesian model selection in ecology is a valuable resource for possible methods of fitting those models.

The model selection methods identified in our review are designed only to identify the best model of those considered, and do not necessarily guarantee that selected models are well-fit to the data. Assessment of the performance of DOMs generally requires additional steps, and the best ways to achieve this are not yet clear. There is no broadly-accepted goodness-of-fit test for dynamic occupancy models, although @mackenzie2004 describes an approach for single-season occupancy models using a parametric bootstrap which can been extended to DOMs; this test is implemented in the *AICcModAvg* and *unmarked* R packages. @kéry2021 describe the test and present an alternative based on separately assessing fit to static and dynamic components of the model. In Bayesian implementations, posterior predictive checks offer means to assess model fit [@gelman2014]. @broms2016 discusses possibilities for model evaluation in the Bayesian context focusing on single-season multi-species occupancy models but extensions of their approach may also be applicable to the DOM. As in other hierarchical models, model evaluation for DOMs can in general can be difficult and somewhat uncertain compared to other model types, as the primary response variable of interest (species occupancy) is a latent variable where the true state is generally not known. Predictive performance evaluation is thus typically based on *observed* occupancy data, where a DOM is used to simulate detection histories to be compared with field survey results.

Perhaps as a result of these difficulties, assessment of model fit and model performance was rare amongst the articles in our sample. Only 19% of studies tested for goodness-of-fit, and just 10% calculated predictive performance. These rates are considerably lower than those reported for SDMs; for which closer to 50% of articles were found to test both fit and performances [@araújo2019].

@@

Studies in our sample were classified according to their objectives as stated by authors to explore the use-cases which the DOM has been applied to (@fig-objectives). These objective categories were non-exclusive, and many studies fell into multiple categories. Across the study period the DOM has been frequently employed to estimate trends in species occupancy, to explore relationships between environmental factors and occupancy, and, increasingly often, to make predictions of occupancy spatially to unsurveyed locations or temporally to hypothetical future conditions. Within each of these broad categories lies even more variation in objectives, emphasising the DOM's flexibility as a tool for making ecological inference in diverse contexts.

Many articles in our sample used the DOM seeking to monitor trends in occupancy state through time ("Estimate trends" in @fig-objectives). These studies include @ahumada2013's paper assessing populations trends of 13 forest mammals and @scott2015's assessment of the conservation status of the endangered flattened musk turtle. These studies offer valuable insights on the state of species across landscapes and through time, demonstrating the DOM's suitability for monitoring oriented projects; including those where multiple species need to be assessed at once. Other articles were more focused on examining the factors which influence species occupancy, either testing pre-specified hypothetical relationships or taking a broader tack to identify drivers of occupancy without preconception. The distinction between the two is important, as it guides which covariates may be considered and how model selection may be used to fit models. Many of these studies target core conservation priorities for their focal species, like @olson2005's early DOM assessing the influence of barred owls on threatened spotted owl. Explorations of these pivotal relationships are important for guiding management action, and may also be used to test the effectiveness of these actions as in @miller2023's study on American Kestrel nest boxes. In scenarios where less is known about species habitat preference, DOMs may be used to examine the influence of a wider variety of factors as illustrated in @huber2017's study testing the relative influence of dozens of habitat covariates on Wood warbler occupancy. In recent years, increasing numbers of articles have used to DOM to generate predictions of species occupancy. As examples, @mcgowan2020 provides projections of future occupancy for the threatened Black rail under multiple management scenarios, and @pollentier2021 generates maps of distributions resembling those made with SDMs, outputs which can immediately be used by managers to inform action.

### 2024-09-23 Randomisation/Randomisation.qmd
Converted most of analysis supplement

1.  ALL=(dynamic occupancy model\*) OR ALL=(occupancy dynamic\$ model\*) OR ALL=(multi\$season occupancy model\*) OR (ALL=(occupancy) AND ALL=(Coloni\$ation) AND ((ALL = (Extinction)) OR (ALL = (Persistence))) AND All=(Detection)) and Ecology or Biodiversity Conservation or Environmental Sciences or Zoology or Evolutionary Biology or Biology or Ornithology or Forestry or Plant Sciences or Environmental Studies or Fisheries or Entomology (Web of Science Categories)
2.  All articles citing MacKenzie et al. 2003

@@

```{r load WOS queries}
keyTerms_datasheet <- read_xlsx("Queries/Final Queries/KeyTerms_A.xlsx",
                                skip = 10) |>
  rbind(read_xlsx("Queries/Final Queries/KeyTerms_B.xlsx",
                  skip = 10)) |>
  select(Title, Year = "Publication Year", Journal = "Source Title", 
         Authors, Citations = "Total Citations", DOI) |>
  mutate(Query = "KeyTerms")

>>>>

1.  ALL=("dynamic\* occupancy model\*") OR TS=(dynamic\* NEAR "occupancy model\*") OR TI=(dynamic\* NEAR "occupancy model\*") OR AB=(dynamic\* NEAR "occupancy model\*") OR ALL=("occupancy dynamic\*") OR ALL=("multi\*season occupancy model\*") OR ALL=("multi-season occupancy model\*") OR (ALL=(occupancy) AND ALL=(coloni?ation) AND (ALL=(extinction) OR ALL=(persistence)) AND ALL=(detect\*)) and Ecology or Biodiversity Conservation or Environmental Sciences or Zoology or Ornithology or Evolutionary Biology or Biology or Marine Freshwater Biology or Forestry or Fisheries or Entomology or Plant Sciences or Environmental Studies (Web of Science Categories)
2.  All articles citing MacKenzie et al. 2003

@@

```{r load WOS queries}
keyTerms_datasheet <- read_xlsx("Queries/Final Queries/Keywords.xlsx",
                                skip = 10) |>
  select(Title, Year = "Publication Year", Journal = "Source Title", 
         Authors, Citations = "Total Citations", DOI) |>
  mutate(Query = "KeyTerms")

### 2024-09-23 _manuscript/Analysis/Analysis.qmd
Converted most of analysis supplement

combinedStudyScale <- siteQuantityPlot / studyDurationPlot
combinedStudyScale <- combinedStudyScale +
  theme(panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA))
combinedStudyScale
ggsave(plot = combinedStudyScale, filename = "Figures/StudyScale.png",
       height = 6, width = 12)
```

>>>>

combinedStudyScale <- siteQuantityPlot / studyDurationPlot
combinedStudyScale <- combinedStudyScale +
  theme(panel.background = element_rect(fill='transparent', color=NA),
        plot.background = element_rect(fill='transparent', color=NA))
ggsave(plot = combinedStudyScale, filename = "Figures/StudyScale.png",
       height = 6, width = 12)
```
